Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
move stuff

This section presents our second contribution, a framework for proving 
correctness of cast representations.
In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
of space-efficient semantics (in the style of CEK machines) indexed by cast 
representations ($ C $). 
In subsection~\ref{secc:framework:bisim}, we prove when $ C $ is 
$ surely \; \text{\lazyD} $, $ \judgeDeval{e}{o} $ if and only $ 
\judgeSeval{C}{e}{o} $, that is, every $ surely \text{\lazyD} $ cast 
representation respects the \lazyD\ cast calculus. 
Proving a similar theorem for \lazyUD\ is in progress.

@@

\subsection{Correctness Proof of Surely \lazyD\ Cast Representations}
\label{ssec:framework:correctness}

\todo[inline]{KC needs to move some content in the next section to here. -KC}

\todo[inline]{Give a high-level summary of the proof.
  The summary should be enough so that the reader knows a bit
  about why you introduce the various definitions below. -JS}

\subsection{\lazyD\ Cast Representations}

In this section we describe a subset of cast representations, where all 
elements implement the \lazyD{} blame strategy. We will show in 
Subsection~\ref{sec:LDHC-correct} that the \lazyD\ HC is in this subset.

@@

\subsection{All Surely \lazyD{} and Monoidic Cast Representations Respect 
\ineffCEKD}

We use bisimulation to proof equivalence between the two machines.
\todo[inline]{Which two machines? -JS}
The bisimulation relation of states ($\eqvDS{C}{s}{s}$) is mostly derived from 
the definitions of \ineffCEKD. Exceptions include the relations from 
continuations to pre-continuations, between continuations, and between values. 
We omit subscripts when there is no ambiguity.

@@

>>>>

This section presents our second contribution, a framework for proving 
correctness of cast representations.
In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
of space-efficient semantics (in the style of CEK machines) indexed by cast 
representations ($ C $). 
In subsection~\ref{secc:framework:correctness}, we prove when $ C $ is 
$ surely \; \text{\lazyD} $, $ \judgeDeval{e}{o} $ if and only $ 
\judgeSeval{C}{e}{o} $, that is, every $ surely\;\text{\lazyD} $ cast 
representation respects the \lazyD\ cast calculus. 
Proving a similar theorem for \lazyUD\ is in progress.

@@

\subsection{Correctness Proof of Surely \lazyD\ Cast Representations}
\label{secc:framework:correctness}

\todo[inline]{Give a high-level summary of the proof.
	The summary should be enough so that the reader knows a bit
	about why you introduce the various definitions below. -JS}
\todo[inline]{KC needs to move some content in the next section to here. -KC}

@@

The bisimulation relation of states ($\eqvDS{C}{s}{s}$) is mostly derived from 
the definitions of \ineffCEKD. Exceptions include the relations from 
continuations to pre-continuations, between continuations, and between values. 
We omit subscripts when there is no ambiguity.

@@

In this section we prove \lazyD\ hypercoercions is correct by showing it, as a 
cast representation, is surely \lazyD\ and a monoid. To use hypercoercion as a 
cast representation in our framework, we need to defined four functions: $ 
cast(T,l,T) $, $ id(T) $, $ seq(c,c) $, and $ applyCast(c,v) $. We have defined 
the first three functions in Section~\ref{sec:hypercoercion-definition}. Now we 
define the $ applyCast(c,v) $

We use bisimulation to proof equivalence between the two machines.
\todo[inline]{Which two machines? -JS}
